---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarytable

The goal of summarytable is to enable users to create simple
summary tables of the frequency of non-numeric variables in a data set
with both the count and proportion of total variables. This package was
created to complete the requirements for assignment B2 of STAT 545B at
UBC.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hjames22/summarytable")
```

##Execution 

All code was prepared in RStudio using R version 4.1.0 (2021-05-18) -- "Camp Pontanezen. All files in this repository can be run and modified using these same programs. 

## Example

This is a basic example which shows you how to solve a common problem:
```{r}
suppressPackageStartupMessages(library(summarytable))
#summary without rows
count_freq_perc(iris, Species, rows = NULL)
```
# A tibble: 3 × 3
  Species    count percentage
  <fct>      <int>      <dbl>
1 setosa        50       33.3
2 versicolor    50       33.3
3 virginica     50       33.3

```{r}
#all groups are equal so will print all three rows. 
count_freq_perc(PlantGrowth, group, rows = 1)
```
# A tibble: 3 × 3
  group count percentage
  <fct> <int>      <dbl>
1 ctrl     10       33.3
2 trt1     10       33.3
3 trt2     10       33.3
